\documentclass[aspectratio=169, table]{beamer}

\usepackage[utf8]{inputenc}
\usepackage{listings} 

\usetheme{Pradita}

\subtitle{MTI104 - IT Services}

\title{Session-14:\\\LARGE{Tips and Tricks for Taking \\the ITIL Exam}}
\date[Serial]{\scriptsize {PRU/SPMI/FR-BM-18/0222}}
\author[Pradita]{\small{\textbf{Alfa Yohannis}}}

\begin{document}

\frame{\titlepage}

\begin{frame}
	\frametitle{Introduction to ITIL Foundation Examination}
	\begin{itemize}
		\item The ITIL Foundation exam is highly sought-after in the IT industry.
		\item It is considered mandatory during employment.
		\item The author attended ITIL v2 training 15 years ago.
		\item Initially, the author did not pass the practice exam.
		\item After extensive preparation, the author succeeded.
		\item The author emphasizes the trainer's role in exam preparation.
		\item This chapter aims to provide an overview of the exam.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Trainer's Experience and Tips}
	\begin{itemize}
		\item The author's experience as a trainer deepened their knowledge.
		\item The author shares tips based on experience.
		\item Over 90% of the author’s students pass on their first attempt.
		\item Many students continue with advanced ITIL courses.
		\item The tips are aimed to help candidates pass the ITIL 4 Foundation exam.
		\item The author understands the exam pattern and question style.
		\item Success in the exam is highly rewarding.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Preparation for ITIL Foundation Exam}
	\begin{itemize}
		\item The book contains all necessary material for the exam.
		\item Stick to the book contents for exam preparation.
		\item Avoid distractions between essentials and extras.
		\item The author shares study habits and tips.
		\item Studying consistently over several days is recommended.
		\item The author structured the book to be read in 7 days.
		\item This approach helps avoid cramming like an engineering student.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Preparation Tips Continued}
	\begin{itemize}
		\item Set a target by scheduling your exam before starting to study.
		\item Most people study after work; 7 days is deemed sufficient.
		\item Unlearn work processes that differ from ITIL.
		\item Take plenty of notes for better understanding.
		\item Familiarize yourself with ITIL definitions and keywords.
		\item Learn through examples provided in the book.
		\item Create your own examples for better comprehension.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Mock Exams for ITIL Preparation}
	\begin{itemize}
		\item Attempt a few mock papers after studying all topics.
		\item Axelos provides a sample paper on their website.
		\item Complete the book before attempting the sample paper.
		\item Use sample papers to gauge understanding.
		\item Real exam patterns are similar to the sample paper.
		\item Answer as many practice questions as possible.
		\item Avoid ITIL V3 questions, focus on ITIL 4.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{On the Exam Day}
	\begin{itemize}
		\item Get plenty of sleep before the exam day.
		\item Schedule the exam in the morning for better focus.
		\item The ITIL exam questions are straightforward.
		\item Be cautious with negatively phrased questions.
		\item Avoid rushing through the exam; take your time.
		\item Verbose answers may often be the correct choice.
		\item There are no negative marks, so attempt all questions.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{FAQs on ITIL-Based Careers}
	\begin{itemize}
		\item ITIL is different from project management.
		\item ITIL is a service management framework.
		\item No IT background is required for ITIL Foundation certification.
		\item ITIL knowledge is essential in IT service organizations.
		\item Software developers can benefit from learning ITIL.
		\item ITIL can facilitate a shift to management roles.
		\item ITIL provides entry-level roles in service operations.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Roles and Progression in ITIL}
	\begin{itemize}
		\item Service desk is a common entry-level role.
		\item Other entry roles include service reporting and access management.
		\item Experience is essential for incident and problem manager roles.
		\item Service operations offer the greatest number of ITIL jobs.
		\item Incident management roles vary by organization.
		\item Change management is often considered part of service operations.
		\item Technical roles in ITIL include DevOps and cloud engineers.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Customer Service and ITIL Roles}
	\begin{itemize}
		\item Customer-facing roles are ideal for those with strong communication skills.
		\item Examples include service-level manager and business relationship manager.
		\item Sales roles also involve showcasing service management capabilities.
		\item The author enjoyed working as a consultant.
		\item Consulting involves finding solutions to business problems.
		\item The author now focuses on architecture and challenging projects.
		\item ITIL knowledge is crucial for roles requiring process integration.
	\end{itemize}
\end{frame}


\end{document}
